\pkg{cubble}: An R Package for Structuring Spatio-temporal Data

### 2022-02-02 main.tex
netcdf example with era5 data

\begin{CodeChunk}
\begin{CodeInput}
R> res <- match_sites(river, climate,
+                    temporal_var_to_match = prcp,
+                    temporal_independent = climate,  
+                    temporal_n_highest = 30,
+                    temporal_min_match = 15)
\end{CodeInput}
\end{CodeChunk}

@@

@@

\caption[Exploring temperature variation using linking of a map and seasonal display]{Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon. The bottom row first selects the lowest temperature in Auguest in the seasonal display. A location in the Tasmania Island is then selected and surprisingly, it is actually warmer than the Thredbo AWS.}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> res <- match_sites(
+   river, climate,
+   temporal_var_to_match = c("Water_course_level" = "prcp"),
+   temporal_independent = "prcp",  
+   temporal_n_highest = 30,
+   temporal_min_match = 15
+ )
\end{CodeInput}
\end{CodeChunk}

@@

Figure \ref{fig:netcdf}

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/research/paper-cubble/figures/netcdf}

\caption[sdf]{sdf}\label{fig:netcdf}
\end{figure}
\end{CodeChunk}

@@

\caption[Exploring temperature variation using linking of a map and seasonal display]{Exploring temperature variation using linking of a map and seasonal display. Each row is a screen dump of the process. The top row shows all locations and all temperature profiles. Selecting a location with high variance on the map produces the plot in the second row. The maximum nad minimum temperature is shown using a ribbon. The bottom row first selects the lowest temperature in Auguest in the seasonal display. A location in the Tasmania Island is then selected and it is actually warmer than the Thredbo AWS.}\label{fig:interactive-linking}
\end{figure}
\end{CodeChunk}
